Monster or Lambda?  A likelihood analysis

### 2023-05-22 inst/monster_vs_lambda.Rmd
slight change

```{r,label=ttrydefflikefvc,cache=TRUE}
Mval <- seq(from=0.0,to=0.65,len=15)
lval <- seq(from=0.2,to=5,by = 0.4) # we need lambda=1 (this is the null)
jj <- as.matrix(expand.grid(M=Mval,lam=lval))
options(use_alabama = FALSE)
L <- apply(jj,1,like2)
```

>>>>

```{r,label=ttrydefflikefvc,cache=TRUE}
Mval <- seq(from=0.01,to=0.65,len=15)
lval <- seq(from=0.2,to=5,by = 0.4) # we need lambda=1 (this is the null)
jj <- as.matrix(expand.grid(M=Mval,lam=lval))
options(use_alabama = FALSE) # setting to TRUE gives a "initial value not feasible" error, go figure
L <- apply(jj,1,like2)
```
